%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% Content Author:
% Michael Holler
% https://github.com/apotheos/resume
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Michael}{Holler}{software developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
7007 Bitterroot Dr.
Plainfield, IL 60586
United States
~
+1 (815) 351 1134
~
\href{mailto:mike@mikeholler.me}{mike@mikeholler.me}
~
\href{http://blog.mikeholler.me}{blog.mikeholler.me}
\href{http://linkedin.mikeholler.me}{linkedin.mikeholler.me}
\section{interests}
NLP
coding standards
restful web services
software architecture
data organization
language design
english language
english literature
technical writing
classics
\section{technologies}
{\color{red} $\varheartsuit$} Python, {\color{red} $\varheartsuit$} Laravel,
Android, Java, Linux,
REST, SQL, Apache,
HTTP, C++, Jenkins,
git, PHP, CodeIgniter
...and growing!
\end{aside}

\section{personal objective}
Coursework placed emphasis on algorithms, theory, application development, and writing.
Notable courses include operating systems, bioinformatics, mobile applications, and NLP.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2010--2014 \\(Expected)}
{Bachelor of Science {\normalfont in Computer Science}}
{North Central College}
{Minors in English Literature and Classics \\
Coursework placed emphasis on algorithms, theory, application development, and writing.
Notable courses include operating systems, bioinformatics, mobile applications, and natural language processing (NLP).}
%------------------------------------------------
\entry
{2013--Now}
{Undergraduate {\normalfont Honors Thesis}}
{North Central College}
{\emph{Automated Back-of-the-Book Indexing} \\
The indexing process is still done by hand, and is very costly and time consuming.
I'm applying NLP algorithms to book indexing to automate the process.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2013--Now}
{VG-Bio}
{Naperville, Illinois}
{\emph{Software Developer} \\
    After a year and a half of interning, I was asked to officially join the team as the sole developer of the first rewrite of VG-Bio's Android application.
    Before completely switching to Android, I helped rearchitect and rewrite the company's REST API, and design a client SDK for the API.
    These projects helped further affirm and develop my capabilities in test-driven development and architecture for large enterprise-level applications.
    I am only just beginning my work in Android, but I expect to further develop and challenge my skills and knowledge.
}
%------------------------------------------------
\entry
{2011--2013}
{VG-Bio}
{Naperville, Illinois}
{\emph{Software Development Intern} \\
    Hired as an intern during Fall term of sophomore year.
    Tasks were:
    \begin{itemize}
        \item Systems administration of virtualized Linux servers
        \item Software integration testing of REST API
        \item Continuous integration with Jenkins
        \item Prototyping
        \item ...and eventually feature development and maintenance of the company's REST API.
    \end{itemize}
    Learned how to work closely with other developers and prioritize programming tasks.
    Developed personal interests in language design, REST, and coding standards by working with many technologies and web services.}
%------------------------------------------------
\entry
{2010--2011}
{North Central College}
{Naperville, Illinois}
{\emph{Computer Science Lab Assistant} \\
Worked with professors to help students with entry-level CS coursework.
Helped students during lab time, and available for one-on-one tutoring.
Teaching yielded the pleasure of helping others and solidified my own knowledge.}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{2011}
{Radioshack}
{Shorewood, Illinois}
{\emph{Sales Associate} \\
Sold phones in Target Mobile kiosk as second job during summer break.
Developed interpersonal skills and troubleshooted technology.
Trusted with working alone on manager's off days.}
%------------------------------------------------
\entry
{2010--2011}
{Target}
{Shorewood, Illinois}
{\emph{Electronics Team Member} \\
Hired as Sales Floor Team Member, but was promoted shortly after starting. Cross-trained for cart attendant, cashier, clothing department, fitting room, flow team, and produce.
Developed important communication and teamwork skills and learned to work as a team to finish while under pressure.
Experiences gained here serve as life lessons today.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS AND HONORS SECTION
%----------------------------------------------------------------------------------------

\section{awards and honors}

\begin{entrylist}
%------------------------------------------------
\entry
{2012}
{Norman and Rose Lewis Endowed Scholarship}
{North Central College}
{Awarded to a handful of commuter students with a high level of community and/or campus involvement, affording those students an opportunity to live on campus for the rest of their college careers.}
%------------------------------------------------
\entry
{2010}
{Presidential Scholarship}
{North Central College}
{Awarded to students entering college with a high high
school GPA and extracurricular involvement.
The most prestigious scholarship offered by NCC.}
%------------------------------------------------
\entry
{2011, 12, 13}
{Medalist}
{ACCA Programming Competition}
{Shared second, third, and second place with NCC's ACCA team in respective years.
ACCA is an Illinois-based inter-school programming competition.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{leadership and involvement}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{Oral Presentation}
{Rall Symposium}
{\emph{Counting Cars: A Journey Into Open Source Hardware}\\
Helped organize and presented research for a cost effective parking tracking system using open source hardware and software.
Research was conducted by members of North Central College's Computer Science club while presiding as President.
One of four speakers in this group presentation.}
%------------------------------------------------
\entry
{2012--Now}
{President}
{Noctrl Computer Science Club}
{Founded Noctrl with three other students.
Organization gives students the opportunity to collaborate on a large project, emulating a small software development company.
Helped lead and develop a REST API for our parking tracking project and often acted as project manager.
Improved leadership, communication, and teaching skills while organizing the club.}
\entry
{2012--Now}
{Member}
{Sigma Tau Delta---English Honor Society}
{Temporarily served as Treasurer in a member's absence.}
%------------------------------------------------
\entry
{2010--Now}
{Editor-in-Chief}
{NCC Kindling}
{Started as a writer freshman year and was published in every publication.
Rose to Secretary sophomore year, became Editor-in-Chief Junior year.
Work with the staff to help write, edit, layout, and publish one issue every ten weeks.
Worked to increase publication budget for the first time in over a decade.
Picked up good organization and planning skills and found working in a tight schedule exciting and challenging.}
%------------------------------------------------
\end{entrylist}
\end{document}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
%
%\section{interests}
%
%\textbf{professional:} data analysis, company profiling, risk analysis, economics, web design, web app %creation, software design, marketing \textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
%
%\section{publications}
%
%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography
%
%\printbibsection{book}{books} % Print all books from the bibliography
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not %containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed %conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing %"keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed %conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%
%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography
%
%\printbibsection{report}{research reports} % Print all research reports from the bibliography
%
%----------------------------------------------------------------------------------------

%\end{document}
